Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-03 prop.tex
prop.tex \section{Conclusion and Discussion} Simplify table...

Number of intervals & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline

@@

Maximum difference between ends of intervals & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline

@@

Number of states in the core & 0 & 0 &  & 1\tabularnewline

@@

Number of states might corresponding to them & $3$ & $2$ & \ldots{} & $1$\tabularnewline

>>>>

Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline

@@

$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline

@@

Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline

@@

Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
